Fluid-mechanical erosion creates anisotropic porous media

### 2022-06-11 docs/PhysicsPaper/StokesErosion.tex
working on sec 3

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). We represent the velocity as the sum
  of a double-layer potential and a combination of Stokeslets and
  rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
boundary. The Stokeslet and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
$\cc_\ell$ is a point inside body $\ell$.

It is convenient to write equation~\eqref{eqn:velocityDLP} in terms of
complex variables. With this reformulation, analytic function theory can
be used to show that a particular quadrature rule achieves spectral
accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
similar notation for $\yy$, and $\nn$. Then, the Stokes double-layer
potential is 
\begin{align}
  \DDD[\eta](x) = \pderiv{}{x} \Re \frac{1}{2\pi i} \int_\Gamma
    \frac{\overline{y \eta(y)}}{x-y} dy + 
\end{align}

  \todo[inline]{Emphasize the complex analysis, rewrite so it isn't
  self-plagirized, compactify which would eliminate, for example,
  equation (15)}
In order to accurately and efficiently compute the Stokes flow governed
  by \eqref{eqn:StokesEq}, we reformulate the system as a boundary
  integral equation (BIE). The boundary integral equations are first
  formulated in $\RR^2$ and then recast in terms of a Cauchy integral.
  The Cauchy integral representation enables a barycentric quadrature
  method to accurately compute the flow intervening between nearly
  contacting bodies, as is required by the dense configurations examined
  in this work.

@@

Applying the same approach as our previous work~\citep{qua-moo2018}, we
start with the double-layer potential 
\begin{align}
  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
  \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:velocityDLP}
\end{align}
where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
is an unknown density function.  We complete the integral equation
formulation by adding the $M$ Stokeslets,
$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
smooth geometry $\Omega$, the solution of the incompressible Stokes
equation with a Dirichlet boundary condition $\ff$ is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:BIE}
\begin{alignat}{3}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \NN_0[\eeta](\xx) \nonumber \\
    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
    \quad &&\qquad\xx \in \bd\Omega, \\
  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
    &&\qquad \ell = 1,\ldots,M.
\end{alignat}
\end{subequations}
Here, the null space associated with the flux-free condition of $\ff$ is
addressed with  $\NN_0$ which is the integral operator with kernel
$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
$\gamma_\ell$, $\ell=1,\ldots,M$.

>>>>

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficiently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). Applying the same approach as our
  previous work~\citep{qua-moo2018}, we represent the velocity as the
  sum of a double-layer potential and a combination of Stokeslets and
  rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
boundary. The Stokeslet and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
$\cc_\ell$ is a point inside body $\ell$. If the density function,
Stokeslets, and rotlets satisfy the second-kind boundary integral
equation
\begin{subequations}
  \label{eqn:FredBIE}
  \begin{alignat}{3}
    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      \quad &&\xx \in \Gamma, \\
    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
    \llambda_\ell &= \int_{\gamma_i} \eeta(\yy) \, ds_\yy, 
      &&\ell = 1,\ldots,M, \\
    \xi_\ell &= \int_{\gamma_i} (\yy - \cc_i)^\perp \cdot 
      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
  \end{alignat}
\end{subequations}
then the representation~\eqref{eqn:velocity}
satisfies~\eqref{eqn:StokesEq}. We solve~\eqref{eqn:FredBIE} by choosing
equispaced collocation points on $\gamma_\ell$ and $\Gamma$, and then
replacing the integrals with quadrature rules. This results in a linear
system with a mesh-independent condition number, and it is solved
iteratively with GMRES.

The accuracy of the method is determined by the accuracy of the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. A quadrature
rule for~\eqref{eqn:velocityDLP} that achieves spectral accuracy writes
the Stokes double-layer potential as a collection of Cauchy integrals
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
\end{align}
The boundary data of $v(x)$ satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense.
Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}

We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use similar
notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the
boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan
curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{align}
  u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
           \Re(v_3'(x)) + \Re(v_4(x)) \\
  u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
           \Im(v_3'(x)) + \Re(v_5(x)),
\end{align}
respectively.

To apply the aforementioned spectrally accurate quadrature rule, we
require the boundary data of the five Cauchy integrals. For $x_0 \in
\gamma$, the boundary data of each of these Cauchy integrals satisfies
the Sokhotski-Plemelj jump relation
\begin{align}
  \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \bd\Omega,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense. For
the Cauchy integral $v_i$, we let $v_i^-$ denote the boundary data that
satisfies~\eqref{eqn:SP}. Once $v_i^-$ is calculated, $v(x)$ and its
derivatives can be determined by the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy,
  \end{alignat}
\end{subequations}

@@

%Applying the same approach as our previous work~\citep{qua-moo2018}, we
%start with the double-layer potential 
%\begin{align}
%  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
%  \frac{1}{\pi}\int_{\bd\Omega} 
%    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
%    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
%%  \label{eqn:velocityDLP}
%\end{align}
%where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
%$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
%is an unknown density function.  We complete the integral equation
%formulation by adding the $M$ Stokeslets,
%$S[\llambda_\ell,\cc_\ell](\xx)$, and $M$ rotlets,
%$R[\xi_\ell,\cc_\ell](\xx)$, where $\cc_\ell$ is a point inside the
%$\ell^{th}$ body~\citep{pow-mir1987}.  Here $\llambda_\ell$ and
%$\xi_\ell$ are the Stokeslet and rotlet strengths, respectively,
%corresponding to the $\ell^{th}$ body.  Then, for any sufficiently
%smooth geometry $\Omega$, the solution of the incompressible Stokes
%equation with a Dirichlet boundary condition $\ff$ is
%\begin{align}
%  \uu(\xx) = \DDD[\eeta](\xx) + 
%    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
%\end{align}
%where the density function, Stokeslets, and rotlets satisfy
%\begin{subequations}
%\label{eqn:BIE}
%\begin{alignat}{3}
%  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
%    \NN_0[\eeta](\xx) \nonumber \\
%    &\quad + \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
%    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), 
%    \quad &&\qquad\xx \in \bd\Omega, \\
%  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
%    \eeta(\yy)\, ds_\yy, &&\qquad \ell = 1,\ldots,M, \\
%  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
%    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy, 
%    &&\qquad \ell = 1,\ldots,M.
%\end{alignat}
%\end{subequations}
%Here, the null space associated with the flux-free condition of $\ff$ is
%addressed with  $\NN_0$ which is the integral operator with kernel
%$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.  In
%this work, $\ff$ is the prescribed velocity, which is equal to $\UU$ on
%the outer wall, $\Gamma$, and equal to zero on the eroding bodies,
%$\gamma_\ell$, $\ell=1,\ldots,M$.
